More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-02-15 2016-Weak-FH-Bisim/WeakBisim.tex
indices in bisim figure, and lotos equivalence exempl rules

 \TODO{Eric: il reste des petits bugs genre $s^{2'}_x$ plutot que
   $s^{2}_x$}

@@

\TODO{Eric: ask Elie, Hubert or others about interesting weak
  equationnal theories for Lotos -- DONE, waiting for answer...}

@@

>>>>

% \TODO{Eric: il reste des petits bugs genre $s^{2'}_x$ plutot que
%   $s^{2}_x$}

@@

\TODO{Eric: ask Elie, Hubert or others about interesting weak
  equationnal theories for Lotos -- DONE, no answer..., so I got some examples from \cite{Lotos:ISO}}

@@

Possible Lotos small examples:

Strong bisim:\\
\centerline{hide \{g\} in a;B  ==  a; hide \{g\} in B  iff gatename(a)$\neq$g}\\
\centerline{hide \{g\} in a;B  ==  i; hide \{g\} in B  iff gatename(a)$=$g}

Weak congruence:\\
\centerline{a;i;B == a;B}\\
\centerline{B[]i;B == i;B}\\
and many others, often not easy to express without syntax for set operations.

Weak equivalence:\\
\centerline{i;B == B}
